% Wm. Blake Sullivan's Resume
% Based on the template by 
% Andrew McNabb

\documentclass[10pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=0.22in,bmargin=0.22in,lmargin=0.50in,rmargin=0.50in,headheight=0in,headsep=0in,footskip=.1in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Wm. Blake Sullivan}
\newcommand{\addr}{713 Meigs St, Rochester, NY 14620}
\newcommand{\phone}{Cell: (251) 586-2749}
\newcommand{\email}{williamblakesullivan@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{bch}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{3pt}
	{\fontfamily{bch}\selectfont\Large#1}
	\begin{itemize}
	\vspace{2pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-2pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location and/or date range
%  Arg 3: Title
\newcommand{\resbigitem}[3]{
	\vspace{-3pt}
	\item
	\textbf{#1} --- #2 \\
	\textit{#3}
}

% A resbigitem is a complex list element for stuff like projects
%  Arg 1: Name of project
%  Arg 2: Date
%  Arg 3: Link or other info
\newcommand{\resaltitem}[3]{
	\vspace{-3pt}
	\item
	\textbf{#1} \hfill #2 \\
	\textit{#3}
}
% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-1pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a list that comes with a resaltitem
\newenvironment{resaltsec}[3]{
	\resaltitem{#1}{#2}{#3}
	\vspace{-1pt}
	\begin{itemize}
}{
	\end{itemize}
}
% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-3pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{bch} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-4pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\normalsize\itshape \addr \hfill \phone \\ \email}

\vspace{15 pt}



%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{ressection}{Summary of Qualifications}

  	\ressubitem{Outgoing college student looking for an evening/nighttime position to pay for classes. Gained extensive interpersonal and customer service skills as tutor, after-school instructor, and freelance web-developer. Proficient with most generic office software and a quick study for any proprietary software.}

  \end{ressection}
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}

	\begin{ressubsec}{Freelance Web Development}{Rochester, NY\hfill July 2017 -- Present}{Self-Employed}
		\ressubitem{Developed and maintained websites for a small number of small-to-medium businesses across the United States.}
		\ressubitem{Maintained consistent productive communication with multiple clients mostly over phone and email due to physical distance.}
	\end{ressubsec}
	
	\begin{ressubsec}{Private Tutoring}{Rochester, NY\hfill September 2017 -- Present}{Self-Employed}
		\ressubitem{Transitioned to private tutoring to reach a wider audience in the greater Rochester area.}
		\ressubitem{Continued with computer programming tutoring while returning to other STEM subjects, primarily AP Physics 1, AP Chemistry, and middle and high school mathematics.}
	\end{ressubsec}
	
	\begin{ressubsec}{Bryx, Inc.}{Rochester, NY\hfill June 2016 -- December 2016}{Software Developer (Co-op)}
		\ressubitem{Planned and developed new web-based applications.}
		\ressubitem{Maintained the public website and dealt with level 1 \& 2 tech support issues.}
	\end{ressubsec}
	
	\begin{ressubsec}{ICanCodeClub}{Rochester, NY\hfill November 2015 -- September 2017}{Coding Instructor \& Lesson Developer}
		\ressubitem{Taught students 1st-12th grade the basics of programming with the use of game design, robotics, and more.}
		\ressubitem{Created and distributed curriculum for 100+ students.}
		\ressubitem{Listened to and incorporated the needs and interests of both students and parents in lessons.}
	\end{ressubsec}
	
	\begin{ressubsec}{Business Information Solutions}{Mobile, AL\hfill June 2012 -- August 2012}{Information Systems Technician Intern}
		\ressubitem{Gained experience in general IT customer service, technical support, and installation.}
		\ressubitem{Worked on a major Ethernet cabling installation of a newly built corporate building.}
	\end{ressubsec}
	
	\begin{ressubsec}{ASMS Tutoring Program}{Mobile, AL\hfill August 2011 -- May 2014}{Volunteer Tutor}
		\ressubitem{Tutored local elementary, middle, and high school students in a variety of topics, primarily STEM-related.}
		\ressubitem{400+ volunteer hours of tutoring over a 3-year period.}
	\end{ressubsec}

\end{ressection}
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

	\begin{ressubsec}{Rochester Institute of Technology}{Rochester, NY\hfill August 2014 -- Present}{Bachelor of Science in Computer Science}
		\ressubitem{Minor in Software Engineering.}
		\ressubitem{Immersion in Public Relations and Advertising.}
		\ressubitem{Member of Computer Science House, a technologically centered living/learning community with a focus on professional advancement.}
	\end{ressubsec}
	
	\begin{ressubsec}{Alabama School of Mathematics and Science}{Mobile, AL\hfill August 2011 -- May 2014}{Concentration w/ Distinction: Computer Science; Concentration: Mathematics}
		\ressubitem{First student in ASMS history to complete a year-long course over the summer (AP Computer Science).}
		\ressubitem{Over 600 hours of volunteer service.}
	\end{ressubsec}
	
	

\end{ressection}
%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{20pt}{\selectfont\Large References: Available upon request}

\end{document}
% vim: set spell tw=150 noet :